### 2014-02-20 paper/retrofit.tex
first draft of semantics

\begin{mathpar}
\inferrule[T-app]
{ } {| conf tS (tE[(\x.te) tv]) --> conf tS (tE[{tv/x} tv]) |}

\and
\inferrule[T-ifTrue]
{ } {| conf tS (tE[if true then te1 else te2]) --> conf tS (tE[te1]) |}

\and
\inferrule[T-ifFalse]
{ } {| conf tS (tE[if false then te1 else te2]) --> conf tS (tE[te2]) |}

\and
\inferrule[T-ref]
{| tS' = tS [ ta mapsto tv ] |} 
{| conf tS (tE[ref tv]) --> conf tS' (tE[tv]) |}
{| fresh ta |}

\and
\inferrule[T-deref]
{| (ta, tv) member tS |}
{| conf tS (tE[!ta]) --> conf tS (tE[tv]) |}

\and
\inferrule[T-ass]
{| tS' = tS [ ta mapsto tv ] |} 
{| conf tS (tE[ta := tv]) --> conf tS' (tE[tv]) |}
\end{mathpar}

@@

>>>>

\begin{mathpar}
\inferrule[T-app]
{ } {| conf tS (intE ((\x.te) tv)) --> conf tS (intE ({tv/x} tv)) |}

\and
\inferrule[T-ifTrue]
{ } {| conf tS (intE (if true then te1 else te2)) --> conf tS (intE te1) |}

\and
\inferrule[T-ifFalse]
{ } {| conf tS (intE (if false then te1 else te2)) --> conf tS (intE te2) |}

\and
\inferrule[T-ref]
{| tS' = tS [ ta mapsto tv ] |} 
{| conf tS (intE (ref tv)) --> conf tS' (intE tv) |}
{| fresh ta |}

\and
\inferrule[T-deref]
{| (ta, tv) member tS |}
{| conf tS (intE (!ta)) --> conf tS (intE tv) |}

\and
\inferrule[T-ass]
{| tS' = tS [ ta mapsto tv ] |} 
{| conf tS (intE (ta := tv)) --> conf tS' (intE tv) |}
\end{mathpar}

@@

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | x | y | ie lop ie | getLabel | setLabel ie
       |  fork ie | send ie ie ie | x, y <= recv. ie ie |  IT te
iE   ::=  iE lop ie | iv lop iE | setLabel iE | fork iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  x, y <= recv. ie ie |  IT tE

tE   ::=  cdots | TI iE

x, y <= brecv . ie @= IT (let te' = TI (x, y <= recv. ie  (IT te')) in te')
\end{code}

\begin{mathpar}
\inferrule[I-getLabel]
{ }
{|
iconf iS (lconf id il tS (iniE (getLabel)), ldots)
-->
iconf iS (lconf id il tS (iniE il), ldots)
|}
\and
\inferrule[I-setLabel]
{ |il canFlowTo il'| }
{|
iconf iS (lconf id il tS (iniE (setLabel il')), ldots)
-->
iconf iS (lconf id il' tS (iniE unit), ldots)
|}
\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|
}
{|
iconf iS (lconf id il tS (iniE (fork (IT te))), ldots)
-->
iconf iS' (lconf id il tS (iniE id'), ldots, lconf id' il tS te)
|}
{|fresh (id')|}
\and
\inferrule[I-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ id' mapsto (il', id,  ie) cons Q ]|
}
{|
iconf iS (lconf id il tS (iniE (send id' il' ie))), ldots)
-->
iconf iS' (lconf id il tS (iniE unit), ldots)
|}
\and
\inferrule[I-recv]
{
| filter il (iS(id)) = (il', id', ie') :: Q'|\\
| iS' = iS[id mapsto Q']|
}
{|
iconf iS (lconf id il tS (iniE (x, y <= recv. ie1 ie2))), ldots)
-->
iconf iS' (lconf id il tS (iniE ({ie'/x,id'/y} ie1)), ldots)
|}
\and
\inferrule[I-noRecv]
{
| filter il (iS(id)) = nil|\\
| iS' = iS[id mapsto nil]|
}
{|
iconf iS (lconf id il tS (iniE (x, y <= recv. ie1 ie2))), ldots)
-->
iconf iS' (lconf id il tS (iniE ie2), ldots)
|}
\and
\inferrule[I-border]
{ }
{| iniE (IT (TI (ie))) --> iniE ie |}
\and
\inferrule[T-border]
{ }
{| intE (TI (IT (te))) --> intE te |}
\end{mathpar}

\caption{IFC language}
\label{fig:ml}
\end{figure}
